Mean and variance functions used to simulate Gaussian data for mean-estimation experiments

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish(c("gaussian_signals.Rmd", "index.Rmd"))

---
title: "Mean and variance functions used to simulate Gaussian data"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

>>>>

---
title: "Mean and variance functions used to simulate Gaussian data for mean-estimation experiments"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---
